\plaintitle

### 2016-09-21 drafts/labor/decomposition.tex
citation fixes

\topic{If decomposition is key to success in crowd work, the question arises: what can, and can't, be decomposed?} 
Moreover, how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better, and the microtask paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers, preventing a single errant submission from impacting the agenda of the work as a whole %, fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense, finer decompositions are seen as more robust --- both to interruptions and errors~\cite{cheng2015break} --- even if they incur a fixed time cost.
At the extreme, recent work has attempted demonstrated microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267} or even tenths of a second~\cite{embracingErrorKrishna}.
%Earlier we discussed \citeauthor{cheng2015break}'s work measuring the impact that interruption has on worker performance \cite{cheng2015break}.%While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components in the form of higher cumulative time to complete (albeit much shorter real time to complete, owing to parallelization)%
However, workers perform better when similar tasks are strung together 
\cite{delayAndOrderLasecki}, or chained and arranged to maximize  the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this, 
%rather than attempt to minimize the error rates in micro--tasks
%, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

\subsubsection{\pieceworkpers}
\citeauthor{Brown01041990} inquired from another direction, asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined, this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically, the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework
\cite{Brown01041990}.

\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories, but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter'',
an icon of \nth{20} century America who represented empowerment and opportunity for women \cite{honey1985creating},
was a pieceworker
\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena
\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

@@

\topic{Piecework researchers enumerate a number of problems with the decomposition of work, and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks, because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible, because \dots
total output is the joint product of varying groups of people''
\cite{bewley1999wages}.

@@

\topic{Where measurement and instrumentation were limiting factors for historical piecework, computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable, but trivial
\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
% cites as
preventing scientific management from being fully utilized,
%the difficulty of tracking work \& workers, no longer exists
%\cite{10.2307/23702539}.}
modern crowd work is measuring and modeling every click, scroll, and keyboard event
\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled, edited, and redeployed
\cite{hu1961parallel}.
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code
\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago
\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

Third, modern crowd work has sliced work to such small scales that the marginal activities
--- things like finding work and cognitive task switching ---
have become large relative to the tasks themselves
\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools, mining equipment, or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own
\cite{hart2013rise}.
The result is that crowd workers are more free agents than historically was the case.
However, because they spend significant time searching for tasks, the piece rate is less a good estimate of take--home earnings than before.

>>>>

\topic{If decomposition is key to success in crowd work, the question arises: what can, and can't, be decomposed?} 
Moreover, how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better, and the microtask paradigm has emerged as the overwhelming favorite~\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers, preventing a single errant submission from impacting the agenda of the work as a whole %, fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense, finer decompositions are seen as more robust --- both to interruptions and errors~\cite{cheng2015break} --- even if they incur a fixed time cost.
At the extreme, recent work has attempted demonstrated microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267} or even tenths of a second~\cite{embracingErrorKrishna}.
%Earlier we discussed \citeauthor{cheng2015break}'s work measuring the impact that interruption has on worker performance \cite{cheng2015break}.%While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components in the form of higher cumulative time to complete (albeit much shorter real time to complete, owing to parallelization)%
However, workers perform better when similar tasks are strung together ~\cite{delayAndOrderLasecki}, or chained and arranged to maximize  the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this, 
%rather than attempt to minimize the error rates in micro--tasks
%, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

\subsubsection{\pieceworkpers}
\citeauthor{Brown01041990} inquired from another direction, asking
what limited the adoption of piecework in industries that otherwise gravitated toward it
(in the case studies he examined, this mostly focused on railway engineers),
ultimately arguing that factors such as the nature of the work design
(specifically, the homogeneity of tasks) and the costs associated with adopting a piecework model
were the major contributing factors that determined the use of piecework~\cite{Brown01041990}.

\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories, but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter'',
an icon of \nth{20} century America who represented empowerment and opportunity for women \cite{honey1985creating},
was a pieceworker~\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

@@

\topic{Piecework researchers enumerate a number of problems with the decomposition of work, and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks, because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible, because \dots
total output is the joint product of varying groups of people''~\cite{bewley1999wages}.

@@

\topic{Where measurement and instrumentation were limiting factors for historical piecework, computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable, but trivial~\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
% cites as
preventing scientific management from being fully utilized,
%the difficulty of tracking work \& workers, no longer exists
%\cite{10.2307/23702539}.}
modern crowd work is measuring and modeling every click, scroll, and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

\topic{A second shift is  
the relative ease with which the metaphorical ``assembly line'' can be changed.}
Historical manufacturing equipment could not quickly be assembled, edited, and redeployed~\cite{hu1961parallel}.
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code~\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago~\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

Third, modern crowd work has sliced work to such small scales that the marginal activities
--- things like finding work and cognitive task switching ---
have become large relative to the tasks themselves~\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools, mining equipment, or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own~\cite{hart2013rise}.
The result is that crowd workers are more free agents than historically was the case.
However, because they spend significant time searching for tasks, the piece rate is less a good estimate of take--home earnings than before.

### 2016-09-21 drafts/labor/discussion.tex
citation fixes

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \cite{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Many of the challenges that \DO~overcame
--- determining trustworthiness, ensuring anonymity, etc\dots
\cite{dynamo} ---
were relatively unique challenges precipitated by the affordances of the Internet, specifically
that people could (and often do) contribute to communities in a one--off manner
\cite{mcinnis2016one}.
The Internet seemed to make this kind of loose affiliation feasible where before it wasn't
\cite{catalyst,dynamo}.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

\subsection{Polarizing Tendencies}\label{sec:polarizationOfCrowdWork}
\topic{It would be easy
to think about the future of crowd work and
end up at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals
\cite{redballoon,crowdworkFuture,vizwiz}; % \ali{and who else should I cite here?}
on the other hand, researchers
warn against crowd work as potentially exploitative sites of dispossession \cite{scholz2012digital},
a site of racial discrimination \cite{edelman2015racial},
and invisible, deeply frustrated workers \cite{turkopticon,bighamHalfWorkday}.

\topic{A uniquely challenging facet of this topic of inquiry is the public attention that this domain has attracted.}
Activists have described speculative work as having
``essentially been turned into modern--day slaves''
\cite{activistsHuffPoLawsuit}.
Meanwhile, advocates describe it as
``a project of sharing
aimed at providing ordinary people
with more economic opportunities and
improving their lives\dots''
\cite{uberPropaganda}.
\ali{these are salient, but with the last paragraph it feels really flimsy.
I'd really like to get this Uber quote in, but
not if it means this paragraph gets that much weaker.}

% \topic{There is, of course, a kernel of truth in everything here.}
\topic{There is evidence to support the claim that
a Dystopian world awaits us at the end of the tunnel.}
The arbitrary nature of on--demand work may permeate our lives, inducing us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371}
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand us;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers
\cite{uberAlgorithm,dynamo,turkopticon}.

\topic{On the other hand, there is some evidence that offers hope.}
Yes, piecework's nascent years were arguably grim, but
they precipitated a century of the strongest labor advocacy the world has ever seen
\cite{hart2013rise,mccallum2013global}.
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation engaged in
the largest labor strike in human history
--- perhaps as many as 150 million
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets,
as some have called for
\cite{futureUnions},
then the future of crowd work may follow
the same trajectory of worker empowerment that piecework \textit{later} found.
\ali{The Internet may make this possible!}
% Arguably the Internet has made collective action on an unprecedented scale much easier.

@@

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''
\cite{bewley1999wages}.
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore; %  unless
% we're actually finding ways to minimize the many forms of costs of switching tasks.
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
empower \ali{I feel like Lily would take some umbrage at this because she seemed to not like the narrative of us researchers just unilaterally bequeathing power upon Turkers (well, Turkers certainly disliked it). Thoughts on refactoring?}
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work \cite{bighamHalfWorkday}
not just because it's possible, but because our community
(of mostly computer scientists)
appreciates the importance of approaches such as participant--observation and ethnography as a whole
\cite{olson2014ways}.
% Whereas piecework didn't have the benefit of Anthropology as we know it or the myriad ways of discovering, learning about, and empowering workers
% What questions are we trying to answer?
% If, as we assumed in
% the previous section on \namerefl{sec:polarizationOfCrowdWork},
% our driving motivation is to empower workers, we

>>>>

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \cite{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''~\cite{scholz2012digital}.
Many of the challenges that \DO~overcame
--- determining trustworthiness, ensuring anonymity, etc\dots~\cite{dynamo} ---
were relatively unique challenges precipitated by the affordances of the Internet, specifically
that people could (and often do) contribute to communities in a one--off manner~\cite{mcinnis2016one}.
The Internet seemed to make this kind of loose affiliation feasible where before it wasn't~\cite{catalyst,dynamo}.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

@@

\subsection{Polarizing Tendencies}\label{sec:polarizationOfCrowdWork}
\topic{It would be easy
to think about the future of crowd work and
end up at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals~\cite{redballoon,crowdworkFuture,vizwiz}; % \ali{and who else should I cite here?}
on the other hand, researchers
warn against crowd work
as potentially exploitative sites
of dispossession \cite{scholz2012digital},
of racial discrimination \cite{edelman2015racial}, and
of invisible, deeply frustrated workers \cite{turkopticon,bighamHalfWorkday}.

\topic{A uniquely challenging facet of this topic of inquiry is the public attention that this domain has attracted.}
Activists have described speculative work as having
``essentially been turned into modern--day slaves''~\cite{activistsHuffPoLawsuit}.
Meanwhile, advocates describe it as
``a project of sharing
aimed at providing ordinary people
with more economic opportunities and
improving their lives\dots''~\cite{uberPropaganda}.
\ali{these are salient, but with the last paragraph it feels really flimsy.
I'd really like to get this Uber quote in, but
not if it means this paragraph gets that much weaker.}

% \topic{There is, of course, a kernel of truth in everything here.}
\topic{There is evidence to support the claim that
a Dystopian world awaits us at the end of the tunnel.}
The arbitrary nature of on--demand work may permeate our lives, inducing us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371}
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand us;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers~\cite{uberAlgorithm,dynamo,turkopticon}.

\topic{On the other hand, there is some evidence that offers hope.}
Yes, piecework's nascent years were arguably grim, but
they precipitated a century of the strongest labor advocacy the world has ever seen~\cite{hart2013rise,mccallum2013global}.
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation engaged in
the largest labor strike in human history
--- perhaps as many as 150 million~\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets,
as some have called for~\cite{futureUnions},
then the future of crowd work may follow
the same trajectory of worker empowerment that piecework \textit{later} found.
\ali{The Internet may make this possible!}
% Arguably the Internet has made collective action on an unprecedented scale much easier.

@@

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}.
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore; %  unless
% we're actually finding ways to minimize the many forms of costs of switching tasks.
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
empower \ali{I feel like Lily would take some umbrage at this because she seemed to not like the narrative of us researchers just unilaterally bequeathing power upon Turkers (well, Turkers certainly disliked it). Thoughts on refactoring?}
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work \cite{bighamHalfWorkday}
not just because it's possible, but because our community
(of mostly computer scientists)
appreciates the importance of approaches such as participant--observation and ethnography as a whole~\cite{olson2014ways}.
% Whereas piecework didn't have the benefit of Anthropology as we know it or the myriad ways of discovering, learning about, and empowering workers
% What questions are we trying to answer?
% If, as we assumed in
% the previous section on \namerefl{sec:polarizationOfCrowdWork},
% our driving motivation is to empower workers, we

### 2016-09-21 drafts/labor/introduction.tex
relationships.tex
added a conclusion.tex file. finished with discussion (i think)
citation fixes

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into de--contextualized, modular blocks
enables computation to hire workers at scale through open calls on the Internet
\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in the work whenever their schedules allow,
with little to no awareness of the broader context of the work, and 
with (often) fleeting identities and associations
\cite{martin2014being,uberAlgorithm}.
In this paper, we use the term on--demand work to join a pair of related phenomena:
\begin{inlinelist}
\item \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work; and
\item \textit{gig work}, typically involving platforms for one--off jobs, like driving, courier services, or administrative support.
\end{inlinelist}
The realization that complex tasks can be accomplished by directing and managing these crowds of workers spurred industry to flock to sites of labor
like AMT and Uber to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g., \cite{bernsteinSoylent,vizwiz,paolacci2010running}).

\topic{As on--demand work has grown far beyond the domain of information work from which it first sprang, it has given rise to an increasingly complicated and conflicted culture amongst both the workers who enable it and the researchers who empower it.}
Originally, \citeauthor{howe2008crowdsourcing} described crowdsourcing in general terms as
``outsourcing [work] to an undefined, generally large group of people in the form of an open call''.
However, for years its instantiation was limited to the utilization of
human intelligence to process data, participate in scientific studies, and perform information work
\cite{CrowdsourcingUserStudies,movieSummarizationWu,
      yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
More recently, crowdsourcing of physically embodied work
--- driving and cleaning, for instance ---
has become a focus for on--demand labor markets
\cite{uberAlgorithm,uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
This growth prompted increasing efforts to understand the workers who gravitate toward these platforms~\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the identification of the sociality of gig work,
and the frustration and disenfranchisement that these systems embody
\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Other work has focused on the \textit{outcomes} of this frustration,
reflecting on the resistance workers express against digitally mediated labor markets
\cite{uberAlgorithm,dynamo}.

\topic{This body of research has sought to answer one central question:
What does the future hold for on--demand work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}
          \item How complex are the goals that crowd work can accomplish?, and
          \item What kinds of goals and industries may eventually utilize it?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item \nameref{sec:decomposition}?
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
\end{enumerate}
This research literature has largely sought to answer these questions by examining the present phenomenon.
So far, it has not offered a framing for holistically explaining
the developments in worker processes that researchers have developed, or
the emergent phenomena in social environments;
nor has any research, to our knowledge,
gone as far as predict future developments.

\subsection{Piecework as a lens to understand crowdsourcing}
% MSB Cutting because it seems like it's just attacking the literature unnecessarily...
% ----
%This large and growing body of research has conversed
%to varying degrees with labor scholarship,
% ...
%To the extent that the research community has explored the boundaries of crowd work,
%it nevertheless has not reflected on the underlying mechanisms determining those boundaries.
%Similarly, work directed toward the decomposition of tasks has begun to appreciate the limits of decomposition,
%but on the whole it hasn't considered the relationship between the decomposition of work and the complexity of work.
% \ali{Mixed feelings about this because I think I'll need to go back into decomposition and
% give a whole thing on \citeauthor{marx2012economic}
% if I bring this up as a real failing of the crowd work research to date.
% Thoughts?}
%While researchers are quickly picking up on the importance of
%the relationships between workers in these platforms,
%this research seems to be unfolding without the benefit of any of
%the inter--personal labor research that has been informing modern work for the better part of a century.
% \ali{Overall: too long? too vague? overstating the shortcomings?}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework}: %\namerefl{sec:pieceworkArc} ---
a work and payment structure which breaks tasks down into standalone contracts,
wherein payment is made for \textit{work output}, rather than for \textit{time}.
Piecework as a metaphor for crowd work is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
\cite{crowdworkFuture}.
But more than this,
the framing of on--demand labor as a re--instantiation of piecework
gives us years of historical material to make sense of the broader research on this new form of work, and allows us to reflect on--demand work through a mature theoretical lens, informed by decades of rigorous, empirically based research.

@@

We organize this paper as follows: we first review the literature on piecework to lay  groundwork and make clear the analogy to on--demand work. Then, we interrogate the three major research questions above from a piecework frame. We will 
% We will look at a broad range of cases under a number of major themes \msb{a broad range under a number of themes is an empty calorie sentence. get specific.}
% we propose as broadly describing the types of research being done in crowd work
% and more generally in what we argue is contemporary piecework.
%We will look at the above questions in crowd work through the lens
%first of the body of research made by crowd work researchers,
%and then of the body of work piecework researchers have offered.
%After validating this lens as a way of reasoning about crowd work and on--demand labor as a whole,
we will identify similarities and differences between piecework as historically understood and
on--demand work as we experience it today.
Finally, we will make predictions of future developments based on how those similarities and differences influenced piecework.
% we will use this perspective to suggest areas of research worth anticipating,
% and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications for researchers and practitioners based on our results.

>>>>

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into de--contextualized, modular blocks
enables computation to hire workers at scale through open calls on the Internet~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in the work whenever their schedules allow,
with little to no awareness of the broader context of the work, and 
with (often) fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.
In this paper, we use the term on--demand work to join a pair of related phenomena:
\begin{inlinelist}
\item \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work; and
\item \textit{gig work}, typically involving platforms for one--off jobs, like driving, courier services, or administrative support.
\end{inlinelist}
The realization that complex goals can be accomplished by directing and managing crowds of workers spurred industry to flock to sites of labor
like AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g., \cite{bernsteinSoylent,vizwiz,paolacci2010running}).

\topic{As on--demand work has grown far beyond the domain of information work from which it first sprang, it has given rise to an increasingly complicated and conflicted culture amongst both the workers who enable it and the researchers who empower it.}
\citeauthor{howe2008crowdsourcing} first described crowdsourcing in general terms as
``outsourcing [work] to an undefined, generally large group of people in the form of an open call''.
However, for years its instantiation was limited to the utilization of
human intelligence to process data, participate in scientific studies, and perform information work~\cite{CrowdsourcingUserStudies,movieSummarizationWu,
      yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
More recently, crowdsourcing of physically embodied work
--- driving and cleaning, for instance ---
has become a focus for on--demand labor markets~\cite{uberAlgorithm,uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
This growth prompted efforts to understand the workers who gravitate toward these platforms~\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the identification of the sociality of gig work,
and the frustration and disenfranchisement that these systems embody~\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Other work has focused on the \textit{outcomes} of this frustration,
reflecting on the resistance workers express against digitally mediated labor markets~\cite{uberAlgorithm,dynamo}.

\topic{This body of research has sought to answer one central question:
What does the future hold for on--demand work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}[label=(\alph*)]
          \item How complex are the goals that crowd work can accomplish?, and
          \item What kinds of goals and industries may eventually utilize it?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item \nameref{sec:decomposition}?
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
\end{enumerate}
This research literature has largely sought to answer these questions by examining the present phenomenon.
So far, it has not offered a framing for holistically explaining
the developments in worker processes that researchers have developed, or
the emergent phenomena in social environments;
nor has any research, to our knowledge,
gone as far as predict future developments.

\subsection{Piecework as a lens to understand crowdsourcing}
% MSB Cutting because it seems like it's just attacking the literature unnecessarily...
% ----
%This large and growing body of research has conversed
%to varying degrees with labor scholarship,
% ...
%To the extent that the research community has explored the boundaries of crowd work,
%it nevertheless has not reflected on the underlying mechanisms determining those boundaries.
%Similarly, work directed toward the decomposition of tasks has begun to appreciate the limits of decomposition,
%but on the whole it hasn't considered the relationship between the decomposition of work and the complexity of work.
% \ali{Mixed feelings about this because I think I'll need to go back into decomposition and
% give a whole thing on \citeauthor{marx2012economic}
% if I bring this up as a real failing of the crowd work research to date.
% Thoughts?}
%While researchers are quickly picking up on the importance of
%the relationships between workers in these platforms,
%this research seems to be unfolding without the benefit of any of
%the inter--personal labor research that has been informing modern work for the better part of a century.
% \ali{Overall: too long? too vague? overstating the shortcomings?}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework}: %\namerefl{sec:pieceworkArc} ---
a work and payment structure which breaks tasks down into standalone contracts,
wherein payment is made for \textit{work output}, rather than for \textit{time}.
Piecework as a metaphor for crowd work is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time~\cite{crowdworkFuture}.
But more than this,
the framing of on--demand labor as a re--instantiation of piecework
gives us years of historical material to make sense of the broader research on this new form of work, and allows us to reflect on--demand work through a mature theoretical lens, informed by decades of rigorous, empirically based research.

@@

We organize this paper as follows: we first review the literature on piecework to lay  groundwork and make clear the analogy to on--demand work. Then, we interrogate the three major research questions above from a piecework frame. 
% We will look at a broad range of cases under a number of major themes \msb{a broad range under a number of themes is an empty calorie sentence. get specific.}
% we propose as broadly describing the types of research being done in crowd work
% and more generally in what we argue is contemporary piecework.
%We will look at the above questions in crowd work through the lens
%first of the body of research made by crowd work researchers,
%and then of the body of work piecework researchers have offered.
%After validating this lens as a way of reasoning about crowd work and on--demand labor as a whole,
We will identify similarities and differences between piecework as historically understood and
on--demand work as we experience it today.
Finally, we will make predictions of future developments based on how those similarities and differences influenced piecework.
% we will use this perspective to suggest areas of research worth anticipating,
% and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications for researchers and practitioners based on our results.
